\TheTitle

### 2016-04-26 linvis.tex
Final Edits

\evantodo {
        \begin{enumerate}
                \item Check captions
        \end{enumerate}
}

@@

This representation works in smaller projects; it enables users to see when changes
are made, when these changes are merged, how each branch is interacting, and the
point where a branch forks from the master branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits
(Figure~\ref{fig:gitk}) losing its visual meaning. In some cases, the Linux kernel
is simply too large for the system to generate a visualization; Github provides a
DAG view for many projects, but is unable to display the visualization for projects
at the scale of the Linux of the kernel (Figure~\ref{fig:gitfail}).  Between 60 and
70k new commits are created for the Linux project every year; According to our
previous work\cite{German2015}, a commit takes a median of 30 days from the time it
is authored until it arrives in the official repository. The snapshot of the kernel
tomorrow may be different than the snapshot from today, containing new commits
authored in the past; distinguishing these new commits from the commits in the
snapshot from today is not trivial.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in Gitk. Commits point
                towards their ancestors, and there is no clear indication of the way
                the travel to reach master. In fact, neither Gitk nor Git is capable
                of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

One major challenge with visualizing the arrival of commits to a repository is that
Git does not store the date that a commit was merged into another branch (including
master). To complicate the problem, the DAG has reference to the ancestors of a
commit (a model necessary for the operation of Git), but developers would prefer
knowing the path a commit followed to reach the master repository. Tracing a path
that any commit followed to the master repository would imply that for any given
merge, it would be possible to know which commits were merged. A user could inspect
the commits that arrived into master within a given time-frame by checking which
commits were merged during that time-frame.

This paper makes two contributions; first, we describe a method of converting the
DAG of the Linux repository into a tree, or \emph{merge-tree} of the repository,
that represents the path used by a commit to reach master; second, we present a
method to inspect and visualize the history of merges in the Linux project using the
merge-tree model.

These methods and visualizations are implemented in a web-based tool called
\tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}.
Our visualizations and tool provide information about the location of any given
commit in its respective merge-tree, the files edited, the modules edited, and the
commit message for a given commit or merge. \tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

Git uses a directed acyclic graph (DAG) as its main data model. In this model, a
commit has one or more ordered parents (ancestors), except the root commits of a
repository which do not have ancestors--Linux git repository has two such commits.
Commits are divided into merge commits, merging two or more branches, and non-merge
commits. Non-merge commits have only one parent, while merge commits have two or
more. The order of the parents matter: the first parent is the branch in which the
merge is being done, while the rest indicate the branches being merged (Git allows
merging multiple branches simultaneously). The second parent is the first branch
merged, the third parent is the second branched merged.

@@

A short example: assume the of commits represented in Figure~\ref{fig:repoEvents}
shows the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in Figure~\ref{fig:repoTree}. Note that the direction of the
edges of the DAG has been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

\begin{figure}[htbp]
        \centering
        \includegraphics[width=.8\columnwidth]{figures/dag.pdf}
        \caption{DAG representation of the commits represented in
                Figure~\ref{fig:repoEvents}. It loses information about what
                repository the commit is performed and through which repositories it
                has passed in its way to master. In fact, the DAG does not even know
                what master is.}
        \label{fig:repoDAG}
\end{figure}

\begin{figure}[htbp]
        \centering
        \includegraphics[width=\columnwidth]{figures/tree.pdf}
        \caption{Merge-tree view of the commits  represented in
                Figure~\ref{fig:repoEvents} showing the path they followed to reach
                master. In this model the successors of each commit represents the
                path followed by that commit to reach master.}
        \label{fig:repoTree}
\end{figure}

@@

Computing the merge-tree from a DAG for any repository may not be possible; however,
certain features of the development process of Linux make it feasible to compute the
merge-tree for the Linux repository. First, the master branch of Linux is maintained
by Linus Torvalds, and only Linus has write access to it. We have verified this
assertion in previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first identifies
the commits made directly to the master branch; whereafter it recursively determines
the shortest path (in terms of time), using the DAG, from each commit to master
using the inverted DAG.

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache when mddev has no gendisk
...
        \end{verbatim}}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one line log messages for the 24
                non-merge commits it merged. The ending ... is part of the log and
                represents that other commits were merged.}
        \label{fig:sampleMerge}
\end{figure}

@@

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October 15 2009 due to the
presence of \textit{foxtrot} commits, which confounds the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and will not work for older merges.

@@

\noindent \textbf{Use-case 1: top-to-bottom approach}\label{sec:usecase1}\\
These are users that are maintaining a section of the kernel and would like to pick
a merge (including all the commits that it merges) and merge it directly into their
current repository. This is useful for reducing the amount of re-implementation
work. For these users, it is important to have the ability to aggregate metadata
about files and modules being effected by the merge.  It is also important for these
users to be able to navigate from the root of the merge-tree toward the leaves.

\noindent \textbf{Use-case 2: bottom-to-top approach}\label{sec:usecase2}\\
These are users that start with a known merge or commit and would like to see what
other changes are being made in commits that are in the same merge, including
knowing the merge-tree they belong to. This is useful to see what other commits are
related to the current commit and how they get collated into merges that eventually
end in master.  This is primarily for maintainers that need to perform some specific
cherry picking of commits. We must provide these users a mechanism for navigating
from a single commit toward the master, allowing them to see other commits that
might be related to it.

@@

In our visualizations, we leverage the Merge-Tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in master,
or is part of a tree which is rooted in the merge that merged it into master.  Each
commit, whether a merge or non-merge, has only one successor; the root of each tree
has none as it was made by Linus Torvalds directly into the master branch. Non-merge
Commits contain the metadata for the changes made. This metadata includes the files
changed, the lines added and removed from each file, the author, the date the commit
was merged into the merge that led to being merged into the kernel, the date the
commit was authored, the patch, and the commit log. Merges contain less metadata,
only storing the author of the merge, the log, the commit date, and the author date,
and potentially, changes necessary to address conflicts during the merge. The
details of the model are outlined in \cite{German2015}.

@@

To navigate and inspect the merge-tree view of the Kernel we created a web-based
tool called \tool. Creating a web-based tool enables users to use the system without
having to install additional software or store a large database, making it more
accessible, more easily maintainable, and platform independent. \tool uses the
following mechanisms to reach our goals of better navigation and better explanation
of the changes.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search.png}
        \caption{Search View. It allows finding commits that were \textbf{merged} in
                a given period or by commit it.}
        \label{fig:search}
\end{figure}

Searching (depicted in Figure \ref{fig:search}) allows a user to filter commits and
merges that are irrelevant. The search mechanism breaks down the results by release
version. A user can further narrow down the search by \textbf{specifying a range of
dates} in which such commits \textbf{were merged by Linus into master, not when the
commits were created.} This distinction is important. We have observed commits that
have taken years to arrive into master after they were originally committed.

@@

If providing commit ID must be specified from the first character to the last
character. For example, the commit `c267548755a184ef97301071300c1739a564e135' is
returned when the user searches for a commit ID of `c26' in the 3.10 Linux kernel.
This commit is a non-merge commit performed, in one of the largest merge-trees of
the kernel; however, this feature will work with any commit ID.  We will use this
commit for showing each of the features of \tool.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search_results_2.png}
        \caption{Search Results. Each is a commit merged in the desired merged
                window.}
        \label{fig:results}
\end{figure}

@@

The first tab displays the full commit log (Figure~\ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using Git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of \tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is good quality. The message for merges may contain a summary of the
commits being merged.  The information within these messages is highly variable, and
is completely dependent on the author's style. As the user moves toward the
top-level merge, the quality of these messages generally improves.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/files_view_2.png}
        \caption{Panels showing the files modified by all the commits that are part
                of this merge.}
        \label{fig:files}
\end{figure}

@@

The modules tab (Figure~\ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by Git, and are not going to
be present in all repositories. In the Linux repository, authors put the module they
are working on in the one-line preview of the log-message; for example: the log
\emph{gcov: add support for FCC 4.9} has updated the \emph{gcov} module (the
coverage testing tool of the kernel). We heuristically extract the module by taking
all text in the log preview of commits until the first colon.  Modules are logical
partitions of the information in the kernel. Depending on where the author was
working, modules can be general, such as ``bluetooth'' and ``wireless'', or can be
quite specific for individual hardware, such as ``ath9k\_hw'' and ``wl1251''. In a
few cases, the author of a commit does not correctly follow this format and the
heuristic approach fails. As with the Files panels, non-merge commits show their
corresponding information, but for merge commits we aggregate all the modules
changed in all the commits that are part of that merge.  The output of this view is
shown in Figure~\ref{fig:modules}.

@@

\begin{enumerate}
        \item List trees are a text-based representation of the merge-tree, and are easy to search and navigate.
        \item Reingold-Tilford trees provide a clear visual represent the tree structure of the merge-tree.
        \item Bubble trees organize the data hierarchically by having the parent node contain the child nodes similarly to tree maps, but
                clearly showing the parent-child relationships between commits and merges.
\end{enumerate}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/list_tree.png}
        \caption{List Tree}
        \label{fig:list_tree}
\end{figure}

@@

The tree can be further extended to include the collapsing of merge nodes. Clicking
on merge nodes will cause them to collapse, only showing parts of the tree that are
of interest to the user.Furthermore, the user can zoom the tree by scrolling the
mouse wheel to see more of the topology of the tree, or to see the details of a
given part of the tree.

@@

Bubble trees are useful for providing a clear visualization of hierarchal
data\cite{Boardman2000}. The bubble tree (Figure~\ref{fig:bubble_tree}) provides a
very clear picture of where a commit is located in the tree hierarchy. The currently
selected commit or merge is colored red, while non-selected merges use a shade of
blue and commits use white.  The depth of the blue colouring is dependent on how
deep in the hierarchy that node is. The root is the lightest blue, and the contained
merges are progressively darker.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/bubble_tree.pdf}
        \caption{Bubble Tree of a large merge, showing in red (the tiny dot close to the middle) the location of a specific commit of interest.}
        \label{fig:bubble_tree}
\end{figure}

@@

The response for the tree is a single object. This object is the root node of the
tree, and may contain an object of children objects in the \verb|children| field,
which are in the same format as the root object. The children object uses the commit
ID as the key.

@@

The file responses contain only the files that the selected merge or commit works
with. The response is a single object in the form of a tree. This object is the root
of the tree, and represents the current merge or commit. If the current position in
the tree is an inner node, the response will contain the child nodes in the
``children'' field, otherwise ``children'' will be an empty list. The format of file
response is as follows,

@@

From a developers point of view, the are two major disadvantages of the DAG model of
Git: a) its edges point backwards, i.e. commits point to their ancestor, not to the
commit that succeeds them on the path to being integrated; and b) the DAG contains
many more edges that are necessary to understand how integration occurred. We
addressed these two issues with the creation of the merge-tree model of the DAG of
Linux. Effectively the merge-tree view recovers the details of each merged branch
into master.

@@

The biggest challenge, however, is computing the merge-tree. Our heuristic
\textbf{only} applies to the Linux kernel repository, and only since July 2009. It
is very likely that the heuristic will not work with other repository, specially
those with fast-forward commits into the master branch (a majority of repositories).
We can address the lack of information by monitoring the state of the repository at
short intervals as we did in \cite{German2015}. This continuous mining of the
repository requires foresight and planning.

Because \tool leverages the merge-tree model of the kernel, it provides mechanisms
and visualizations that other tools are unable to produce.It gives us the ability to
see how commits are being merged into the kernel, allowing us to better understand
how code is integrated into the kernel.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/042dd_tree.png}
        \caption{Merge Tree View \dmg{this Figure is unreadable. Any chance you can make the text bigger?}}
        \label{fig:tree_view}
\end{figure*}

Our goal was to build a tool to enable maintainers to effectively navigate and
browse the changes performed to the kernel over the period of a release.  Achieving
this goal includes removing information that does not pertain to the area of the
kernel that the user is interested in. In Figure~\ref{fig:dag_view} and
Figure~\ref{fig:tree_view} we can visually compare the results returned from Gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. Note that Gitk has no way to show or recognize that this
is a merge into the master branch.

@@

Many tools work to address the issues in communication between developers in
inter-team collaboration work. Codebook \cite{Begel2010} uses a data mining
technique  to determine the developer of a piece of code, the program manager who
wrote the specification for the code, and the program managers and developers on the
team who were working together. Hipikat\cite{Cubranic2005} is another tool with a
focus on communication. Where codebook focuses on developers working on a project,
Hipikat is focused on enabling easier integration of new developers to a project by
providing them with easily-searchable artifacts of the changes made. Codebook is
useful for pairing a contributor with the original developer; however, the developer
may not have worked with the piece of code in years. A Hipikat program may provide
more information to the maintainer as it records the artifacts of why certain
design decisions were made when they were made using other tools like Bugzilla and
CVS. In both cases, our goal includes providing a summary of the topology of the
kernel repository through a visual tree.

>>>>

@@

This representation works in smaller projects; it enables users to see when changes
are made, when these changes are merged, how each branch is interacting, and the
point where a branch forks from the master branch. In large modular projects, like
the Linux kernel, the DAG becomes a mess of merges and commits
(Figure~\ref{fig:gitk}) losing its visual meaning. In some cases, the Linux kernel
is simply too large for the system to generate a visualization; Github provides a
DAG view for many projects, but is unable to display the visualization for projects
at the scale of the Linux of the kernel (Figure~\ref{fig:gitfail}).  Between 60k and
70k new commits are created for the Linux project every year; according to our
previous work\cite{German2015}, a commit takes a median of 30 days from the time it
is authored until it arrives in the official repository. The snapshot of the kernel
tomorrow may be different than the snapshot from today, containing new commits
authored in the past; distinguishing these new commits from the commits in the
snapshot from today is not trivial.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/gitk.png}
        \caption{A sample DAG view of commits from Linux in Gitk. Commits point
                towards their ancestors and there is no clear path from the commit
                to the merge with the master branch. In fact, neither Gitk nor Git
                are capable of showing what commits were done in master.}
        \label{fig:gitk}
\end{figure}

@@

One major challenge with visualizing the arrival of commits to a repository is that
Git does not store the date that a commit was merged into another branch, including
the master branch. To complicate the problem, the DAG only has references to the
ancestors of a commit (a model necessary for the operation of Git), but maintainers
would prefer knowing the path a commit followed to reach the master repository.
Tracing a path that any commit followed to the master repository would imply that
for any given merge, it would be possible to know which commits were merged. A user
could inspect the commits that arrived into the master branch within a given
time-frame by checking which commits were merged during that time-frame.

This paper makes two contributions; first, we describe a method of converting the
DAG of the Linux repository into a tree, or \emph{merge-tree} of the repository,
that represents the path used by a commit to reach the master branch; second, we
present a method to inspect and visualize the history of merges in the Linux project
using the merge-tree model.

These methods and visualizations are implemented in a web-based tool called
\tool\footnote{\tool is currently available at \url{http://li.turingmachine.org}}.
Our visualizations and tool provide information about the location of any given
commit in its respective merge-tree, the files edited, the modules edited, and the
commit message for a given commit or merge. \tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all merges
made by Linus that contain a commit or inner merge that matches the search query, or
just the commits and merges that match the query.

@@

Git uses a directed acyclic graph (DAG) as its main data model. In this model, a
commit has one or more ordered parents (ancestors), except the root commits of a
repository which do not have ancestors--Linux git repository has two such commits.
Commits are divided into merge commits, merging two or more branches, and non-merge
commits. Non-merge commits have only one parent, while merge commits have two or
more. The order of the parents matter: the first parent is the branch in which the
merge is being done, while the rest indicate the branches being merged (Git allows
merging multiple branches simultaneously). The second parent is the first branch
merged, the third parent is the second branched merged, etc.

@@

A short example: assume the commits represented in Figure~\ref{fig:repoEvents} shows
the sequence of events in a repository. In this case, commits are performed in
various repositories and branches. The DAG representation of the commits is shown in
Figure~\ref{fig:repoDAG}. Notice that the DAG loses information about the master
branch and the repository that the master branch is part of. The merge-tree view of
this DAG is visible in Figure~\ref{fig:repoTree}. Note that the direction of the
edges of the DAG have been inverted, instead of pointing from the child to the
ancestors, it points from the ancestor to its successors, forming a path to the
master branch. Also note that the DAG has been simplified, showing only a single
edge on the path to master for any commit.

@@

\begin{figure}[htbp]
        \centering
        \includegraphics[width=.8\columnwidth]{figures/dag.pdf}
        \caption{DAG representation of the commits represented in
                Figure~\ref{fig:repoEvents}. The DAG loses information about which
                repository the commit is performed in and through which merges it
                has passed on its way to the master branch. The DAG does not even
                distinguish the master branch from other branches.}
        \label{fig:repoDAG}
\end{figure}

\begin{figure}[htbp]
        \centering
        \includegraphics[width=\columnwidth]{figures/tree.pdf}
        \caption{Merge-tree view of the commits  represented in
                Figure~\ref{fig:repoEvents} showing the path they followed to reach
                the master branch. In this model the successors of each commit
                represents the path followed by that commit to reach the master
                branch.}
        \label{fig:repoTree}
\end{figure}

@@

Computing the merge-tree from a DAG for any repository may not be possible; however,
certain features of the development process of Linux make it feasible to compute the
merge-tree for the Linux repository. First, the master branch of Linux is maintained
by Linus Torvalds, and only Linus has write access to it. We have verified this
assertion in previous research~\cite{German2015}. We have developed a heuristic that
is presented in Algorithm~\ref{fig:alg}. In short, the algorithm first identifies
the commits made directly to the master branch; whereafter it recursively determines
the shortest path (in terms of time), using the DAG, from each commit to the master
branch using the inverted DAG.

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache when mddev has no gendisk
...
        \end{verbatim}}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one-line log messages for the 24
                non-merge commits it merged. The ending ``...'' is part of the log
                and represents that other commits were merged.}
        \label{fig:sampleMerge}
\end{figure}

@@

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October, 15, 2009 due to the
presence of \textit{foxtrot} commits, which confounds the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and will not work for older merges.

@@

\noindent \textbf{Use-case 1: top-to-bottom approach}\label{sec:usecase1}\\ These
are users that are maintaining a section of the kernel and would like to pick a
merge (including all the commits that it merges) and merge it directly into their
current repository. This is useful for reducing the amount of re-implementation
work. For these users, it is important to have the ability to aggregate metadata
about files and modules being effected by the merge. Also, it is important for these
users to be able to navigate from the root of the merge-tree toward the leaves.

\noindent \textbf{Use-case 2: bottom-to-top approach}\label{sec:usecase2}\\
These are users that start with a known merge or commit and would like to see what
other changes are being made in commits that are in the same merge, including
knowing the merge-tree they belong to. This is useful to see what other commits are
related to the current commit and how they get collated into merges that eventually
end in the master branch. This is primarily for maintainers that need to perform
some specific cherry picking of commits. We must provide these users a mechanism for
navigating from a single commit toward the master branch, allowing them to see other
commits that might be related to their original commit.

@@

In our visualizations, we leverage the Merge-Tree model described in
Section~\ref{sec:mergetree}. In this model each commit is either already in the
master branch, or is part of a tree which is rooted in the merge that merged it into
the master branch.  Each commit, whether a merge or non-merge, has only one
successor; the root of each tree has none as it was made by Linus Torvalds directly
into the master branch. Non-merge commits contain the metadata for the changes made.
This metadata includes the files changed, the lines added and removed from each
file, the author, the date the commit was merged into the merge that led to being
merged into the kernel, the date the commit was authored, the patch, and the commit
log. Merges contain less metadata, only storing the author of the merge, the log,
the commit date, and the author date, and potentially, changes necessary to address
conflicts during the merge. The details of the model are outlined in
\cite{German2015}.

@@

To navigate and inspect the merge-tree view of the kernel we created a web-based
tool called \tool. Creating a web-based tool enables users to use the system without
having to install additional software or store a large database, making it more
accessible, more easily maintainable, and platform independent. \tool uses the
following mechanisms to reach our goals of better navigation and better explanation
of the changes.

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search.png}
        \caption{Search View allows filtering commits that were merged in a given
                period, filtering by author, keyword, or commit ID.}
        \label{fig:search}
\end{figure}

Searching (depicted in Figure \ref{fig:search}) allows a user to filter commits and
merges that are irrelevant. The search mechanism breaks down the results by release
version. A user can further narrow down the search by specifying a range of dates in
which such commits were merged by Linus into the master branch, not when the commits
were created. This distinction is important. We have observed commits that have
taken years to arrive into the master repository after they were originally
committed.

@@

If the user is searching by commit ID, ID must be specified from the first character
to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches for a
commit ID of `c26' in the 3.10 Linux kernel. This commit is a non-merge commit
performed in one of the largest merge-trees of the kernel; however, this feature
will work with any commit ID.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/search_results_2.png}
        \caption{Search Results. Each table entry is a commit merged in the desired
                merged window.}
        \label{fig:results}
\end{figure}

@@

The first tab displays the full commit log (Figure~\ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using Git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of \tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is of good quality. The message for merges may contain a summary of
the commits being merged.  The information within these messages is highly variable,
and is completely dependent on the author's style. As the user moves toward the
top-level merge, the quality of these messages generally improves.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/files_view_2.png}
        \caption{Panel showing the files modified by all the commits that are part
                of this merge.}
        \label{fig:files}
\end{figure}

@@

The modules tab (Figure~\ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by Git, and are not going to
be present in all repositories. In the Linux repository, authors put the module they
are working on in the one-line preview of the log-message; for example: the log
\emph{gcov: add support for FCC 4.9} has updated the \emph{gcov} module (the
coverage testing tool of the kernel). We heuristically extract the module by taking
all text in the log preview of commits until the first colon.  Modules are logical
partitions of the information in the kernel. Depending on where the author was
working, modules can be general, such as ``bluetooth'' and ``wireless'', or can be
quite specific for individual hardware, such as ``ath9k\_hw'' and ``wl1251''. In a
few cases, the author of a commit does not correctly follow this format and the
heuristic approach fails. As with the Files panel, non-merge commits show their
corresponding information, but for merge commits we aggregate all the modules
changed in all the commits that are part of that merge.  The output of this view is
shown in Figure~\ref{fig:modules}.

@@

\begin{enumerate}
        \item List trees are a text-based representation of the merge-tree, and are easy to search and navigate.
        \item Reingold-Tilford trees provide a clear visual representation of the tree structure of the merge-tree.
        \item Bubble trees organize the data hierarchically by having the parent node contain the child nodes similarly to tree maps, but
                clearly showing the parent-child relationships between commits and merges.
\end{enumerate}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/list_tree.png}
        \caption{List tree view of merge 73287a43cc79ca06629a88d1a199cd283f42456a}
        \label{fig:list_tree}
\end{figure}

@@

The tree can be further extended to include the collapsing of merge nodes, only
showing parts of the tree that are of interest to the user. Furthermore, the user can
zoom the tree by scrolling the mouse wheel to see more of the topology of the tree,
or to see the details of a given part of the tree.

@@

Bubble trees are useful for providing a clear visualization of hierarchical
data\cite{Boardman2000}. The bubble tree (Figure~\ref{fig:bubble_tree}) provides a
very clear picture of where a commit is located in the tree hierarchy. The currently
selected commit or merge is colored red, while non-selected merges use a shade of
blue and commits use white.  The depth of the blue colouring is dependent on how
deep in the hierarchy that node is. The root is the lightest blue, and the contained
merges are progressively darker.

\begin{figure}
        \centering
        \includegraphics[width=0.47\textwidth]{figures/bubble_tree.pdf}
        \caption{Bubble Tree of merge 73287a43cc79ca06629a88d1a199cd283f42456a,
                showing in red (the tiny dot close to the middle) the location of
                the commit highlighted in Figure~\ref{fig:zoomed_tree}.}
        \label{fig:bubble_tree}
\end{figure}

@@

The response for the tree is a single object. This object is the root node of the
tree, and may contain an object of children sub-tree objects in the \verb|children|
field, which are in the same format as the root object. The children object uses the
commit ID as the key.

@@

The file responses contain only the files that the selected merge or commit works
with. The response is a single object in the form of a tree. This object is the root
of the tree, and represents the current merge or commit. If the current position in
the tree is an inner node, the response will contain the child nodes in the
\verb|children| field, otherwise \verb|children| will be an empty list. The format of file
response is as follows,

@@

From a developers point of view, the are two major disadvantages of the DAG model of
Git: a) its edges point backwards, i.e. commits point to their ancestor, not to the
commit that succeeds them on the path to being integrated; and b) the DAG contains
many more edges that are necessary to understand how integration occurred. We
addressed these two issues with the creation of the merge-tree model of the DAG of
Linux. Effectively the merge-tree view recovers the details of each merged branch
into the master branch.

@@

The biggest challenge, however, is computing the merge-tree. Our heuristic only
applies to the Linux kernel repository, and only since July 2009. It is very likely
that the heuristic will not work with other repositories, specifically those with
fast-forward commits into the master branch (a majority of repositories). We can
address the lack of information by monitoring the state of the repository at short
intervals as we did in \cite{German2015}. This continuous mining of the repository
requires foresight and planning.

Because \tool leverages the merge-tree model of the kernel, it provides mechanisms
and visualizations that other tools are unable to produce. It gives us the ability to
see how commits are being merged into the kernel, allowing us to better understand
how code is integrated into the kernel.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/042dd_tree.png}
        \caption{Merge tree topology for the same merge as in
                Figure~\ref{fig:dag_view}.}
        \label{fig:tree_view}
\end{figure*}

Our goal was to build a tool to enable maintainers to effectively navigate and
browse the changes performed to the kernel over the period of a release. Achieving
this goal includes removing information that does not pertain to the area of the
kernel that the user is interested in. In Figures~\ref{fig:dag_view} and
\ref{fig:tree_view} we can visually compare the results returned from Gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. Note that Gitk has no way to show or recognize that this
is a merge into the master branch.

@@

Many tools work to address the issues in communication between developers in
inter-team collaboration work. Codebook \cite{Begel2010} uses a data mining
technique  to determine the developer of a piece of code, the program manager who
wrote the specification for the code, and the program managers and developers on the
team who were working together. Hipikat\cite{Cubranic2005} is another tool with a
focus on communication. Where Codebook focuses on developers working on a project,
Hipikat is focused on enabling easier integration of new developers to a project by
providing them with easily-searchable artifacts of the changes made. Codebook is
useful for pairing a contributor with the original developer; however, the developer
may not have worked with the piece of code in years. A Hipikat program may provide
more information to the maintainer as it records the artifacts of why certain
design decisions were made when they were made using other tools like Bugzilla and
CVS. Neither tool is sufficient in meeting our goals to provide a summary of the
topology of the kernel repository through a visual tree.
